---
title: "Are AI values in groups equal or not?"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Required packages
```{r warning=FALSE, message=FALSE}
library(here)
library(dplyr)
library(BEST)
```

# Data
```{r}
dat = read.csv(here("Data", "SBSN.csv"))
dat1 = dat %>% select(AI = AI0.005, disease)

NPSLE = dat1 %>% filter(disease == "NPSLE")
SLE   = dat1 %>% filter(disease == "SLE")
VM    = dat1 %>% filter(disease == "VM")
MS    = dat1 %>% filter(disease == "MS")
HC    = dat1 %>% filter(disease == "HC")

NPSLE1 = NPSLE$AI
SLE1   = SLE$AI
VM1    = VM$AI
MS1    = MS$AI
HC1    = HC$AI

```

# 2-group comparison
## SLE-NPSLE
```{r message=FALSE}
SLE_NPSLE = BESTmcmc(NPSLE1, SLE1)
```


```{r}
summary(SLE_NPSLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(SLE_NPSLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(SLE_NPSLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## VM-NPSLE
```{r message=FALSE}
VM_NPSLE = BESTmcmc(NPSLE1, VM1)
```


```{r}
summary(VM_NPSLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(VM_NPSLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(VM_NPSLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## MS-NPSLE
```{r message=FALSE}
MS_NPSLE = BESTmcmc(NPSLE1, MS1)
```


```{r}
summary(MS_NPSLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(MS_NPSLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(MS_NPSLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## HC-NPSLE
```{r message=FALSE}
HC_NPSLE = BESTmcmc(NPSLE1, HC1)
```


```{r}
summary(HC_NPSLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(HC_NPSLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(HC_NPSLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## VM-SLE
```{r message=FALSE}
VM_SLE = BESTmcmc(SLE1, VM1)
```


```{r}
summary(VM_SLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(VM_SLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(VM_SLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## MS-SLE
```{r message=FALSE}
MS_SLE = BESTmcmc(SLE1, MS1)
```


```{r}
summary(MS_SLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(MS_SLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(MS_SLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


## HC-SLE
```{r message=FALSE}
HC_SLE = BESTmcmc(SLE1, HC1)
```


```{r}
summary(HC_SLE, 
        credMass = 0.8,
        ROPEm = c(-0.01, 0.01))
```


```{r}
plot(HC_SLE, credMass = 0.8, ROPE = c(-0.01, 0.01))
```


```{r}
plotAll(HC_SLE, 
        credMass=0.8, 
        ROPEm=c(-0.01,0.01),
        ROPEeff=c(-0.2,0.2), 
        compValm=0.5)
```


# References
1. John K. Kruschke and Mike Meredith (2021). BEST: Bayesian Estimation 
    Supersedes the t-Test. R package version 0.5.3.
    https://CRAN.R-project.org/package=BEST  

2. Kruschke, J. K. 2013. Bayesian estimation supersedes the t test. 
    Journal of Experimental Psychology: General 142(2):573-603. 
    [doi: 10.1037/a0029146](https://doi.org/10.1037/a0029146)  

3. [BEST package vignettes](https://cran.r-project.org/web/packages/BEST/vignettes/BEST.pdf)  

4. [How to Compare Two Groups with Robust Bayesian Estimation in R](https://mvuorre.github.io/posts/2017-01-02-how-to-compare-two-groups-with-robust-bayesian-estimation-using-r-stan-and-brms/)  

5. [Group comparisons](https://bookdown.org/marklhc/notes_bookdown/group-comparisons.html)  

6. [ROPE](https://cran.r-project.org/web/packages/bayestestR/vignettes/region_of_practical_equivalence.html)  

7. [Group comparisons 2](https://bookdown.org/content/3686/bayesian-approaches-to-testing-a-point-null-hypothesis.html#are-different-groups-equal-or-not)  

# Note
## 1
```{r}
library(bayestestR)
?rope
```
