---
title: Something related to Bayesian data analysis
#author:
#  - name: Alice Anonymous
#    email: alice@example.com
#    affiliation: Some Institute of Technology
#    footnote: 1
#  - name: Bob Security
#    email: bob@example.com
#    affiliation: Another University
#  - name: Cat Memes
#    email: cat@example.com
#    affiliation: Another University
#    footnote: 2
#  - name: Derek Zoolander
#    email: derek@example.com
#    affiliation: Some Institute of Technology
#    footnote: 2
#address:
#  - code: Some Institute of Technology
#    address: Department, Street, City, State, Zip
#  - code: Another University
#    address: Department, Street, City, State, Zip
#footnote:
#  - code: 1
#    text: "Corresponding Author"
#  - code: 2
#    text: "Equal contribution"
#abstract: |
#  This is the abstract.
#
#  It consists of two paragraphs.

#journal: "An awesome journal"
#date: "`r Sys.Date()`"
bibliography: SBSN.bib
#linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
---
```{r, include=FALSE}
library(HDInterval)

data <- read.csv(here::here("final_cutoff", "cp_VEleni_final.csv"))

burnin = 1000000
iter = 1000000
thin = 10

cp_95 <- hdi(data$cp, credMass = 0.95)
cp_89 <- hdi(data$cp, credMass = 0.89)
```


# Methods
The cut-off of biomarker AI and its predictive values were determined using a Bayesian model described by @Vradi2018. 
The model can be expressed as:  
\[Y|X \sim Bernoulli(p)\]
\[
p(x) = P(Y = 1|X = x) = 
\left\{
    \begin{array}{lr}
          p_1 = P(Y = 1|X \le cp) = 1 - NPV, & \text{if } x \le cp\\
          p_2 = P(Y = 1|X > cp) = PPV, & \text{if } x > cp
    \end{array}
\right.
\]  
The binary response variable _Y_ took the value 1 when a patient had NPSLE and 0 otherwise. 
_X_ was the continuous measurement of the biomarker AI. 
In this study, the positive predictive value (PPV) of the cutoff _cp_ was expected to $\ge$ 70%, while the negative predictive value (NPV) was $\ge$ 50%. 
Thus, prior distributions of 1-NPV and PPV were chosen as follows: 
\[p_1 \sim Uniform(0, 0.5)\]
\[p_2 \sim Uniform(0.7, 1)\]
The Bayesian analysis was carried out in SAS Studio [@SAS2015] through PROC MCMC, which uses Markov chain Monte Carlo (MCMC) algorithm. 
The model was run for a total of `r (burnin + iter)` iterations. The first `r burnin` iterations were discarded as burn-in. The remaining were kept 1 in `r thin` samples (thinning) to reduce autocorrelation. 
The MCMC representativeness and accuracy were assessed by trace plot, sample autocorrelation, effective sample size (ESS), and Monte Carlo standard error (MCSE).  

# Results
- Diagnostic results  
    - Trace plot of all parameters mixed well => showed no potential problem with convergence.  
    - Sample autocorrelation of all parameters dropped quickly to zero with increasing lag.  
    - ESS of all parameters were > 17500. (recommended: > 10000)  
    - MCSE of all parameters were < 0.0059.  
=> Conclusion: MCMC chains were stable and accurate.  

- Posterior distribution summary  
  - report: the mean and 95% highest density interval (HDI) of cp, p1, p2. (in Table **Posterior Summaries and Intervals** of the file **Results_cutoff_VEleni_final.pdf**)  

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(kableExtra)

data <- read.csv(here::here("final_cutoff", "cp_VEleni_final.csv"))

data %>% 
          select(cp, p1, p2) %>%
          gather(para_name) %>%
          group_by(para_name) %>%
          summarise(median = median(value),
                    mean = mean(value)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Parameter", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "ll",
	      caption = "this table is used to compare mean and median value when necessary")

```


  - 95% HDI of cutoff value was in range `r cp_95[1]`-`r cp_95[2]` but 89% HDI of cutoff was in this small range `r cp_89[1]`-`r cp_89[2]`.  

# Caption of Figure:  
Fig1. Summary of posterior distribution of the cutoff and its predictive value (1-NPV and PPV). 
The vertical red dotted lines denote the median of the distribution.  

# Supplementary
## Diagnostic results  
## SAS MCMC code  

```
PROC import datafile="/path/to/data.csv"
DBMS=csv out=Data replace;
RUN; 


PROC MCMC 
	data=Data outpost=Dataoutput 
		nbi=1000000 
		nmc=1000000
		thin=10
		seed=1
		diag=all
		monitor=(p1 p2 cp I w); 
PARMS cp1 cp2 p1 p2 w I; 
prior cp1 ~ uniform(1,10); 
prior cp2 ~ normal(5,sd=1); 
hyperprior I ~ beta(1,1); 
prior w ~ binary(I); 
cp = w*cp1 + (1-w)*cp2; 
prior p2 ~ uniform(0.7, 1);
prior p1 ~ uniform(0, 0.5);
p = (AI<=cp)*p1 + (AI>cp)*p2; 
model Y ~ binary(p);
RUN;
```

References {#references .unnumbered}
==========


