---
title: "Comparing two groups using `brms` package"
output: html_notebook
---

Required packages
```{r warning=FALSE, message=FALSE}
library(here)
library(dplyr)
library(brms)
```

# Data
```{r}
dat = read.csv(here("Data", "SBSN.csv"))
dat = dat %>% 
          select(AI = AI0.005, disease) %>%
          filter(disease == "NPSLE" | disease == "SLE")
```

# Model
Fit the model by `STAN` via `brms` package then saving fitted model object in 
the external `brms_compare_BEST.rds` file via the `saveRDS()` function.  
```{r message=FALSE}

mod = brm(bf(AI ~ disease, sigma ~ disease),
          family = student,
          data = dat,
          chains = 4,
          iter = 50000,
          warmup = 25000,
          cores = 4,
          seed = 12345,
          file = "brms_compare_BEST")

```

Reload `mod` object without re-fitting the model.  
Choose file `brms_compare_BEST.rds`  
```{r}
mod = readRDS(file.choose())

```

# Interpretation
```{r}
summary(mod)
```

*Intercept: Group 0's mean a.k.a. mean of AI in NPSLE  
*sigma_Intercept:
*diseaseSLE: the difference between groups  
*sigma_diseaseSLE: SD of the difference between groups  

`diseaseSLE` = -0.38 => AI in SLE less than in NPSLE 0.38  

# Conclusions
Results from `BEST` package and `brms` package are nearly identical.  



# Reference
[How to Compare Two Groups with Robust Bayesian Estimation in R](https://mvuorre.github.io/posts/2017-01-02-how-to-compare-two-groups-with-robust-bayesian-estimation-using-r-stan-and-brms/)

