---
title: "Cutoff - VEleni - without outliers"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

## Required packages
```{r}
library(here)
library(dplyr)
library(ggplot2)
library(cowplot)
```

## Import data
```{r}
dat = read.csv(here("Data", "cp", "cutoff_data.csv"))
```

## Possible outliers
outlier: an observation that has a relatively large or small value compared to the majority of observations.  

Determine possible outliers by `Cleverland dotplot`
```{r}
# Cleverland dotplot
dotchart(dat$AI, xlab = "AI")

# Determine possible outliers
which(dat$AI > 10)
```

Possible outlier: observation 4.    

Remove observation 4, then save new data set as `cutoff_outlier.csv`.  
```{r}
dat %>% slice(-4) %>% 
          write.csv(file = "Data/cp/cutoff_outlier.csv", 
                    row.names = FALSE)
```

## Running MCMC in SAS Studio
- Step 1: Upload data set `cutoff_outlier.csv`  
- Step 2: Create SAS program `cutoff_VEleni_outlier.sas`  
- Step 3: Run `cutoff_VEleni_outlier.sas`  
- Step 4: Check Errors, Warnings, Notes in `LOG`   
- Step 5: Check convergence of MCMC chains  
- Step 6: Save results as PDF: 
          RESULTS -> Open in a new browser tab -> (right-click) Save as PDF...  
- Step 7: Save SAS data output: 
          Libraries -> My Libraries -> WORK -> (right-click) Export  
- Step 8: Plot cp, p1, p2 in R by `ggplot2`

## Plot Cutoff-p1-p2 posterior distribution

```{r}
cpplot = function(data, 
                  para,
                  xtitle,
                  ytitle = "Density",
                  histbin = 0.2,
                  densize = 0.9,
                  dencolor = "dimgray",
                  ...)
{fig = ggplot(data, aes(x=para)) + 
          # histogram
          geom_histogram(aes(y = ..density..),
                         binwidth = histbin,
                         color = "black",
                         fill = "white") +
          # add mean line
          geom_vline(aes(xintercept=median(para)), 
                     color = "red",
                     size = 1) +
          # add density line
          geom_density(size = densize,
                       color = dencolor) + 
          labs(x = xtitle,
               y = ytitle) + 
          theme_bw() +
          theme(panel.border = element_blank(), 
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), 
                axis.line = element_line(colour = "black"), 
                axis.text = element_text(colour = "black"), 
            ...)
fig
}
```

## p1 ~ uniform(0, p2)
### Data
```{r}
datp2 = read.csv(here("Data", "cp", "cp_VEleni_p2_outlier.csv"))

```

### Plot
```{r warning=FALSE, message=FALSE} 
cp_p2= cpplot(datp2, datp2$cp,
              xtitle = "Cutoff")
cp_p2

p1_p2 = cpplot(datp2, datp2$p1,
               histbin = 0.01,
               xtitle = "1 - NPV")
p1_p2

p2_p2 = cpplot(datp2, datp2$p2,
               histbin = 0.005,
               xtitle = "PPV")
p2_p2

cowplot::plot_grid(cp_p2, p1_p2, p2_p2,
                   ncol = 1)
```

## p1 ~ uniform(0, 0.5)
### Data
```{r}
dat05 = read.csv(here("Data", "cp", "cp_VEleni_05_outlier.csv"))

```

### Plot
```{r warning=FALSE, message=FALSE}
cp_05= cpplot(dat05, dat05$cp,
              xtitle = "Cutoff")
cp_05

p1_05 = cpplot(dat05, dat05$p1,
               histbin = 0.005,
               xtitle = "1 - NPV")
p1_05

p2_05 = cpplot(dat05, dat05$p2,
               histbin = 0.005,
               xtitle = "PPV")
p2_05

cowplot::plot_grid(cp_05, p1_05, p2_05,
                   ncol = 1)
```

